% Make contract sections paragraphs
\titlespacing*{\section}
{0pt}{3em}{1em}

\renewcommand*{\thesection}{\S\ \arabic{section}}

% The introduction
\begin{center}
\amivfairtitle
\bigbreak
\begin{huge}
Contract
\end{huge}
\medbreak
between
\bigbreak
\end{center}

\vspace{2cm}

% Contract partners
\begin{minipage}[t]{0.4\textwidth}
\textbf{Exhibitor}
\bigbreak
\companyname\\
\companyaddress\\
\companycity\\
\companycountry
\end{minipage}%
\begin{minipage}[t]{0.2\textwidth}
and
\end{minipage}%
\begin{minipage}[t]{0.4\textwidth}
\textbf{Organizer}
\bigbreak
\amivname\\
\amivaddress\\
\amivpostal\ \amivcity
\end{minipage}

\vfill
% Start of contract
\section*{Preamble}

Every year, `AMIV an der ETH' (AMIV at ETH) organises a two-day-long jobfair at ETH
Zurich. The fair's goal is to bring together the participating companies and students
from the departments of `Electrical Engineering and Information Technology',
`Mechanical and Process Engineering' and `Management, Technology and Economics'.

\newpage
\section{Subject matter of the contract}
\subsection{Booth}

\companyboothchoice\hfill\companyboothprice
\companyboothinfo

\subsection{Participation date(s)}

\companydatechoice

\subsection{Additional options and pakets}

\companyextrachoice

\section{Price}

The price includes additional costs such as electricity and an internet connection, as
well as refreshments (sandwiches and beverages) for the exhibitor.

\section{VAT}

All prices are quoted net of VAT, but the organizer reserves the right to add VAT if appropriate.

\section{Payment}

The billing amount is to be paid within 30 (thirty) days after invoice reception.

\section{Cancellation Policy}
\begin{enumerate}
	\item In the event of the exhibitor cancelling their participation, a compensation fee will be levied by the organizer
	\begin{enumerate}
		\item Cancellation 30 days or more before participation date:\\
			30\% of the full amount due,
		\item Cancellation 20 days or more before participation date:\\
			50\% of the full amount due,
		\item Cancellation 10 days or more before participation date:\\
			75\% of the full amount due,
		\item Cancellation 9 days or less before participation date:\\
			100\% of the full amount due.
	\end{enumerate}

	\item Additional options and pakets (\S 1.3) remain untouched by a cancellation.
\end{enumerate}

\section{Deadlines}

\begin{enumerate}
\item Necessary information for the fair guide has to be provided by the exhibitor within
the deadlines specified by the organizer; delays may result in omission of the
exhibitor in the fairguide, on the website etc.
\item Booths must be set up between 08:30 AM and 10:30 AM on the participation day.
\item Booths must be dismantled by 7 PM on the participation day.
\end{enumerate}

\section{Contact}

The organization of the event is carried out by:
\bigbreak
\begin{tabular}{l}  % Tabular for identical layout to info below
\textbf{\amivname}\\
\amivaddress\\
\amivcity\\
\end{tabular}
\bigbreak
\begin{tabular}{l l}
Organisation: & Kommission Kontakt\\
President: & \amivkontaktpresident\\
E-Mail: & \amivemail\\
\end{tabular}
\bigbreak
\noindent We remain at your disposal should you need any further information or assistance.

\section{Data Storage}

The organizer will save the data and information collected over the course of the business relationship. The organizer will only use the collected data
in the context of this contract.


\section{Disclaimer of Liability}

The organizer is only liable for damages produced through negligent behavior. This especially excludes force majeure.


\section{Language}

The whole text of the present Contract has been written in German and English, 
both versions being deemed authentic, but for legal purposes the text in German 
is to be given priority of interpretation.

\section{Severability Clause}

The unenforceability or invalidity of any clause in this Agreement shall not 
have an
impact on the enforceability or validity of any individual clause. Any unenforceable
or invalid clause shall be regarded as removed from this Agreement to the extent of its
un enforceability and invalidity. Therefore, this Agreement shall be interpreted and
enforced as if it did not contain the clause in question.

\section{General}
\begin{enumerate}
\item Swiss law applies.
\item Exclusive place of jurisdiction for all disputes is Zurich.
\end{enumerate}

% End of contract, add fields to sign
\vfill
\noindent
\begin{minipage}[t]{0.45\textwidth}
\amivcity, the \hrulefill

\bigskip\noindent
\amivname\\
represented by

\vspace{4em}
\hrulefill

\amivkontaktpresident

Kommission Kontakt, President
\end{minipage}%
\hspace{0.1\textwidth}
\begin{minipage}[t]{0.45\textwidth}
\makebox[8em]{\hrulefill}, the \hrulefill

\bigskip\noindent
\companyname\\
represented by

\vspace{4em}
\hrulefill

\companycontact\vphantom{Ensure correct height.}\\

\end{minipage}
